Quantum Mechanics Assignment Six

### 2016-02-24 quantum/latex/a7.tex
h

\section{2: Spectroscopy Numbers}

>>>>

This was an interesting problem. It was good to go over how the relativistic fine-
structure corrections are derived, especially how to deal with a $1/\hat{r}$
operator. At first I was confused about how to deal with an inverse operator, but
then I realized that it was just a normal operator, like $\hat{r^2}$. Exploiting
the fact that the complex conjugate Hamiltonian acts on bras the same way that the
normal Hamiltonian acts on kets was another important method to solving this problem.\\

\section{2: Spectroscopy Numbers}
Here we discuss the spectroscopic labels and splitting we see in the figure in the
problem.\\

The labels are kind of like spectroscopic notation. The upper term (3d, 2p, etc...) is
the n and $\ell$ number for the state, where $\ell$ is translated into alphabet
notation. The subscript is the
